Pillar A1

### 2019-02-18 Baby Recommender.Rmd
rearranges sections, expands to all students

#
##Transcripts of selected students
target_transcript <- d_transactions$taken_PF_HL %>%
  filter(
    sequenceID %in% s1
  ) %>%
  select(-`Period (additional)`, -`Period (additional bis)`, -`Concentration (additional)`)

@@

For a single student:
```{r truncated transcript}

##Matching rules to students:
###Taken
```{r will take}
taken_match <- AR$taken %>%
  left_join(sample_transcript, by = c("lhs"="item"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

@@

>>>>

#
##Transcripts of selected students
target_transcript <- d_transactions$taken_PF_HL %>%
  filter(
    sequenceID %in% s1
  ) %>%
  select(-`Period (additional)`, -`Period (additional bis)`, -`Concentration (additional)`) %>%
  select(sequenceID, eventID, item, item_PF, item_HL, Grade)

#c("Course ID", "Course Title.x", "Cluster", "n_ILO", "n_assessment", "Assessments Covered", "n_AoD", "AoD Covered", "Concentration", "Missing from ILO File", "Most Recent Catalogue", "Type", "Letters", "Number", "Level", "sequenceID", "Course Title.y", "Grade", "Year_numerical", "Period", "Number Repeated Attempt", "Academic Year", "Fail", "eventID", "PF", "HL", "item", "item_PF", "item_HL")

@@

For all students
```{r truncated transcript}

course_sample_size <- 8

#
##Truncated prospective transcript
prospective_transcript <-target_transcript %>% 
  group_by(sequenceID) %>%
  top_n(course_sample_size, eventID)
#
##Truncated student transcript
sample_transcript <- prospective_transcript %>% 
  group_by(sequenceID) %>%
  top_n(5, eventID) %>%
  arrange(sequenceID)

#
##Only prospective courses
prospective_transcript <- prospective_transcript %>%
  anti_join(sample_transcript, by = c("sequenceID", "eventID", "item", "item_PF", "item_HL", "Grade"))  %>%
  arrange(sequenceID)

# TO DO: basic- doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
##Matching rules to students:
###Taken
```{r will take}
# very basic, doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
taken_match <- AR$taken %>%
  full_join(sample_transcript, by = c("lhs"="item"))%>%
  drop_na() %>%
  group_by(sequenceID, rhs) %>%
  summarise(RHS_vote= n())  %>%
  arrange(sequenceID,desc(RHS_vote))

recommendations <- taken_match %>%
  group_by(sequenceID)         %>%
  filter(row_number(RHS_vote) %in% 1:3) %>% #can use top_n
  arrange(sequenceID)          %>%
  select(sequenceID, RHS_vote, everything())

recommendations

```
####Check
```{r evaluation}
recommendations %>%
  full_join(prospective_transcript, 
            by= c("sequenceID"="sequenceID","rhs"="item")
            ) %>% # this should not be left join.
  drop_na()
```

@@

TEST: For a single student:
```{r truncated transcript}
